LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-09-28 text/draft.tex
First route draft done

\gsection{Wait 1}

TODO

@@

@@

She instantly drops off her plate of food, rises from her makeshift seat, and jumps to hug me. Her warm arms vigorously lock behind my back in a frank embrace, bringing my face mere centimeters of her own.\\

\dcomment{
	First actual appearance of Antiope, with a simple zoom for the close-up
}

This is a purely friendly greeting, yet it takes all my will to keep my heartbeat in check. After an ephemeral eternity, she releases me and speaks.\\

\speaker{Antiope} "Ambrosia! Where have you been? You just disappeared after your performance at the poetry contest. I was unable to find you anywhere. That's so unlike you!"\\

I savor my own name in her mouth like it was the divine nectar it refers to. I feel guilty for it, but I enjoy far too much the fact that she did remark that I was not there anymore, and that she cared about it.\\

I smile timidly. I escaped for her, to have some time alone to think about the future of both of us at peace. But is that something I should really say so bluntly.

\begin{itemize}
	\item \glink{Approaching the rift}{Say that I needed the solitude}
	\item \glink{Sport}{Avoid the subject and praise her for her performance this morning}
\end{itemize}

@@

I barely recognize my own voice. It sounds so... depressed. She blinks, grabs my hand, her face suddenly serious, concerned.\\

\speaker{Antiope} "Ambrosia, are you alright? Is there something wrong? You're not acting like yourself. Are you sick? Has someone done something to you?"\\

@@

\gsection{Sport}

TODO

\gsection{It's nothing}

TODO

@@

>>>>

@@

\dcomment{
	Close-up on the eyes? "Special attack" style, with a narrow rectangle in the middle of the screen
}

@@

She half rises, hemmed in her movements by the food plate on her knees, but I stop her with a sign of the hand and sit at her side at the extremity of the narrow bench, pushing her a little. She holds back a grin and I show a mischievous smile. Her military mind had naturally chosen a position from which she could have easily fled. An advantage I just negated, cutting her way out.\\

\dcomment{
	First appearance of Antiope sprite (little by little?)
}

From so close, it's obvious I'm at least half a head taller than her, which never ends to surprise me. She looks big in everyday life, thanks to her headstrong confidence and athletic build, but is actually pretty average when using factual measurements.

\dcomment{
	Drop Antiope's name, using her athletic physique as a starting point.
}

My shoulder brushes against her own, my robe touching the skin left nude on that place by her old style of clothing. Some judge it barbaric. She judges it practical. I judge it sexy as...\\

\speaker{Antiope} "Ambrosia, where have you been? I looked after you when the party started, but you were nowhere to be found."\\

Her voice returns me to the real world. Sort of. Before answering, I savor my own name in her mouth like it is the divine nectar it refers to. She pronounces it with a slight but unmissable accent, giving it a strange sonority unique to her, a cute quirk I have learned to enjoy.\\

I display a pale smile. I could easily answer truthfully. I could as easily direct the conversation in another direction. Or even more easily remain silent.

\begin{itemize}
	\item \glink{Approaching the rift}{Truth}
	\item \glink{Sport}{Distraction}
	\item \glink{Silence}{Silence}
\end{itemize}

@@

I barely recognize my own voice. It sounds so... depressed. Barely a whisper, filled with shrills and holes, all music gone from it. She blinks, her face suddenly serious, concerned.\\

\speaker{Antiope} "Ambrosia, are you alright? You're not acting like yourself. Has someone done something to you?"\\

@@

\gsection{Silence}

I remain silent, dismissing the question with a mysterious smile and a wave of the hand. She does not insist, and hands me a bunch of pastries wrapped in a small piece of fabric. I accept one and starts eating slowly, with little mouthfuls, not in a hurry to speak. She devoured one with far less decorum and I remark that she has piled up enough food to feed a whole army. Following my glance, she displays a all teeth out smile.\\

\speaker{Antiope} "Eat like a wolf. As much as you can while you can, so to be ready for when you will have nothing eat."\\

Typical. She knows a seemingly endless list of rules, proverbs, little tales implying carnivorous animals and survival. This one is actually pretty tame compared to the most bloody, dark and depressing you've heard from her.\\

And she does live by them. Always stuffing herself to the limit each time the food is free. It's a wonder how she keeps her physique, even if her stupidly hard and harsh daily routine probably helps a lot.\\

Yet another habit one could find ridiculous at first, but touching once you realized it has been forcefully implemented into her, a scar from a childhood she refuses to talk about.\\

She engulfs plate after plate, swallowing exactly one full cup of wine between each of them with a fascinating regularity. Even if the alcohol is heavily watered, she clearly already took more than her share, and I worry she will soon fall in an advanced state of inebriation.

\begin{itemize}
	\item \glink{Stupor}{Let her do that she wants}
	\item \glink{Sobriety}{Stop her}
	\item \glink{Drunk}{Join her}
\end{itemize}

@@

\gsection{Stupor}

\dcomment{
	Not uninteresting scene, but need to be delayed later... Or at least the transition is too brutal. Insist on the time passing and Antiope letting herself loose
}

With each new plate, with each new cup, her movements slow down, her actions are more hesitant, more imprecise. Until finally, her febrile hands let go a ripped tomato, which splashes into the ground.\\

She looks at the stain with absent eyes for several couples of seconds, and suddenly she rises from her seat and starts stumbling in the approximate direction of the nearest exit.\\

Seeing her in pain, I immediately stand up and help her. My left arm around her shoulders, I guide and support her all the way out. As we laboriously walk together, trying not to bump into anybody, I can feel her erratic, hot, wine-laden breath against my neck, her moist skin under my palm. She really is in a poor state.\\

After an eternity, we finally meet the fresh air of the outside. A beautiful garden shows itself before us. It was full of people earlier, but many hours have passed since, the night is now at its coldest, and the place has been almost deserted.\\

I drag Antiope away to a bench near a fountain. The stone is slightly humid, extremely cold, and I worry that letting her lie on it could be an incredibly stupid idea. But she just sits – collapses – there.\\

She remains like this, motionless, expressionless, her eyes staring at her feet, for at least a good minute. Then she finally lets go a weak groan, straightens up her head to look at me and speaks with difficulty.\\

\speaker{Antiope} "I may have overdone it."\\

I feel fire rising inside my throat. Anger.\\

\speaker{Ambrosia} "Yes. Yes you did."\\

\speaker{Antiope} "I didn't realize I had already drunk so much. We celebrated a first time after this morning games and..."\\

\speaker{Ambrosia} "Antiope! That's not the problem."\\

I almost yelled the last sentence. I am furious, burning with a sore rage.\\

\speaker{Ambrosia} "That's not the first time that happened! You eat and you drink as if trying to killing yourself from asphyxia and drowning! I don't care about your proverbs, this is just sick."\\

She stares at me with empty eyes. Stammers a few syllables. Stands up. Go to the pond. Splashes her face with cold water. Returns to the bench. Sits up again, looking a little better this time. And answers.\\

\speaker{Antiope} "You know of this Spartan story with the fox?"\\

\speaker{Ambrosia} "The one where a little boy would rather have his insides rip apart by the fox he stole than to be caught red-handed? Yes, I know of it."\\

\speaker{Antiope} "Yes, that one. What do you think of it?"\\

I hesitate, disoriented with the sudden change of subject.\\

\speaker{Ambrosia} "A gory tale tailored for a quick spread and a long-lasting legacy. Bloody, violent, shocking, everything a good urban legend needs to endure. It can also be interpreted as much as a tribute to the courage of Spartans as a denunciation of the cruelty of their education methods, and thus is told by both admirers and the enemies of this city."\\

\speaker{Antiope} "Do you think it's based on a true story?"\\

\speaker{Ambrosia} "I... don't know. Probably not, even if it appears to take its roots in some real Spartan customs."\\

\speaker{Antiope} "Yes, teaching how to steal to your future soldiers is actually a pretty rounded idea."\\

Antiope is speaking quickly, too quickly, each word mashing with the next, her accent more pronounced than ever.\\

\speaker{Antiope} "A marching army is made of thousands of people, all needing to eat. And most often than not, for the core of the troops, after a few days, all their rations are gone and they have to live off the land. A ridiculous euphemism for stripping bare any field, any tree, any granary, any house. For a nobody in such cohorts, the art of soulless plundering is perhaps more important than knowing how to handle your weapon. The main fight may never come for many political reasons, but your stomach still aches every day."\\

\speaker{Antiope} "And, sometimes, an expedition can turn \emph{really} bad. The war may have trailed for so long that literally every edible thing around has already be ransacked. Far more people have already died from the many diseases corrupted water and rotten food bring than on the actual battlefield.\\

\speaker{Antiope} "Then the suffering army can be crushed utterly regardless of its many sacrifices, pushed into a retreat so chaotic that many small isolated groups are left behind, and must now make their way back on their own, in hunger and fear. For a perfect agony, you can even add some rain or snow."\\

\speaker{Antiope} "A lot more will die. But quite a number will also somehow survive. Among them, some will have sacrificed all morality, decency, humanity to escape the sirens of Inferno. They succeeded in returning to their home, but they will never be the same, their behavior forever changed."\\

Antiope suddenly stops talking and shuts her mouth tight. She looks frightening, her eyes burning with a dark hate I have never seen before.\\

\begin{itemize}
	\item \glink{Posttraumatic}{Comfort her}
	\item \glink{Fleeing the past}{Keep silent}
\end{itemize}

\gsection{Posttraumatic}

I softly put my hand on her shoulder.\\

\speaker{Ambrosia} "It's okay."\\

Antiope's fingers lock on my wrist with tremendous strength and she pushes back my arm like she was deflecting some sword blow, getting to her feet in the same movement. My heart starts beating furiously again, but from fear this time. I see death in her eyes, an unsheathed killing instinct.\\

\speaker{Ambrosia} "Antiope, please..."\\

My voice is but a whisper, but seems to have an effect nonetheless. Some emotions return to her sight, and she releases me. I move back a few steps, my hurt wrist pressed against my chest, the skin having turned red where she pressed it.\\

\speaker{Antiope} "I'm sorry..."\\

Her voice is pitiful, far from her ordinary confidence, her face has crumbled into a mask of distress.\\

\speaker{Antiope} "I didn't want to..."\\

\speaker{Ambrosia} "Are you ready to speak without trying to break my arm?"\\

My own voice is cold as ice. My wrist hurts, but my heart hurts far more. I feel betrayed.\\

Antiope freezes, looks at me attentively. I can only imagine what she is seeing, but when she answers, it's with a single, weak, almost inaudible, syllable.\\

\speaker{Antiope} "Yes."\\

We walk to another part of the garden. It's no less cold, just a little less humid, but I couldn't stand to remain near that damn pond for one more minute. We find another bench, and sit in such a way we're facing each other, me with my legs on the stone and my arms around my knees, Antiope in an awkward three-quarters position, her legs balancing and her torso turned in my direction.\\

\speaker{Antiope} "I'm sorry."\\

\speaker{Ambrosia} "For?"\\

\speaker{Antiope} "For my behavior. For having attacked you in all possible manners when you were just trying to prevent me from hurting myself. For being an idiot in general."\\

\speaker{Ambrosia} "And more precisely?"\\

\speaker{Antiope} "It's hard to put into words... I sometimes feel like the scorpion desperately resisting the impulse to sting. I'm a living pile of stupid, dangerous reflexes and biases. Do you know that the first nights we passed together, I barely got any sleep because I didn't completely roll out you would rob me as soon as I close my eyes? Despite everything and anything proving me you were no bandit?"\\

You try to appear unfazed, but this piece of information is indeed new to you.\\

\speaker{Antiope} "I'm fighting it every day that... \emph{paranoia}. I don't know if it's the proper word. Sort of fear of everything. But when I'm stressed, exhausted, drunk, my impulses get the best of me."\\

\speaker{Antiope} "Usually, I manage to keep them in check regardless, or at least to hide myself when they're at their worst. But today has been a long day. I have been tired since midday and partially drunk since early afternoon."\\

She pauses.\\

\speaker{Antiope} "I understand this is no excuse, only explanation. I know my weaknesses first and foremost. Some of these troubles may have been implanted into me by circumstances and bad teaching but it's still my responsibility that they do not hurt others. Especially those I care about."\\

I sigh. lengthily.\\

\speaker{Ambrosia} "Why didn't we have this conversation earlier?"\\

\speaker{Antiope} "I don't really know. The last times I went overboard... Sometimes, I manage to escape these talks... And the other times..."\\

\speaker{Ambrosia} "Yes. I know. I'm the one who fled."\\

I look at her right in the eyes, seeing my own face reflected in her pupils. Yes, there are a few times when I just kept silent on Antiope sick habits. Not only about alcohol, but also concerning her violent behavior. Today the first time she ever hurt me, but there were several mornings when her face or fists were bearing the marks of fights she got herself into. And I never dared to ask.\\

We're a nice couple of cowards and idiots.\\

\begin{itemize}
	\item \glink{Declaration}{Now}
	\item \glink{Friends}{Never}
\end{itemize}

\gsection{Fleeing the past}

Time passes.

Slowly.

Antiope does not budge a muscle.

I don't dare moving either.\\

We stay like this for minutes? Hours? I can't say. I just know that after an eternity in the cold, Antiope finally stands up and whispers:\\

\speaker{Antiope} "Thanks."\\

And on these words, she walks away into the night.\\

\glink{Masks}{Continue}

\chapter*{Endings}

\gsection{Masks}

\dcomment{
	Abrupt transition to the next morning
}

I feel groggy. I suppose I have slept. At least, I awoke on a straw mattress with no memory of a couple of hours. But I don't feel rested, not even close. With a lasting headache, I walk to the place Antiope and me agreed to meet once the party will be over.\\

And indeed, she is there. I'm relieved but also a little afraid of what will come next. And her reaction is the worst: Nothing. She does not act any different. She is exactly the same as she was two days prior.\\

Is she pretending or was everything what happened last night so unimportant to her? I can't say. And I don't want to know. She is there. We're talking like friends, still sharing the same intimacy. And I'm too much of a coward to risk breaking that again.\\

So I put on my own mask, I imbued myself of my own role, and I greet her cheerfully.\\

\dcomment{
	To rework, but I think there is something to do with the imagery of masks and theaters
}

\gsection{Declaration}

I readjust my position, closing the distance between me and Antiope. Our faces are only separated by the width of a hand when I speak again.\\

\speaker{Ambrosia} "Antiope. You are not perfect. You have problems and you indeed made them worse by trying to solve them entirely by yourself. But you're not the only one. The world is full of idiots doing stupid things because they refuse to open their heart. Me included."\\

I swallow. Hard.\\

\speaker{Ambrosia} "The moment is not perfect, but it will never be. I cannot ask you to be honest with me when I'm not telling you the whole truth myself."\\

\speaker{Ambrosia} "Antiope."\\

\speaker{Ambrosia} "I love you."\\

Antiope's reaction is refreshingly simple. A flash of surprise succeeded by an extraordinary deluge of embarrassment. She turns almost comically pink from all the blood rising up to her head and mumbles some incomprehensible words. I smile warmly.\\

\speaker{Ambrosia} "Take your time. No need to hurry."\\

I feel calm. I have done it. The arrow has been shot, and there is nothing I can do to change its course now.\\

Antiope mumbles a little more, then breathes deeply and tries to compose an answer that makes some sense.\\

\speaker{Antiope} "I... First, thank you for telling me. I understand these are little words it takes a lot of courage to pronounce. Especially in our situation."\\

\speaker{Antiope} "I'm somehow flattered but... You're a extraordinary friend, a good \emph{travel} companion but... I have no romantic interest in you."\\

Silence.\\

\speaker{Antiope} "I'm sorry."\\

I try to keep my voice cool and articulate.\\

\speaker{Ambrosia} "I guessed so. Thank you for your frankness."\\

More awkward silence.\\

\speaker{Ambrosia} "If I may ask... Could you give me some time alone? I need it."\\

\speaker{Antiope} "Are you sure?"\\

\speaker{Ambrosia} "Certain. I will see you tomorrow, don't worry."\\

\speaker{Antiope} "Fine, I will go to sleep then. I've done enough idiocies for the night."\\

She stands up. Hesitates. Looks at me. I give her an encouraging nod. She utters some last civilities, and finally departs, not without looking back a few times, worry painted on her face. I disarm her with a smile each time.\\

Only when I'm certain she is far from here do I allow myself to break into tears.\\

\dcomment{
	Discrete transition
}

I'm late. By at least one hour. I already woke up late, but it's the time I spent cleaning my face which really put me in. The minutes flew by when I was erasing all traces of sadness, tiredness, despair from my face with a professional care, water, soap and an appropriate use of cosmetics. But now I look fresh and ready again.\\

Antiope is at the meeting point, and by the look of her own face, she did not take any action to wipe out the excesses of yesterday and has been worryingly waiting for quite a bit now. I greet her happily and she welcomes me with open arms and a touch of awkwardness.\\

As we walk together on the road, the distance between us becomes even more obvious. Or perhaps on the contrary it's the new proximity which is strange. Objectively, before, we never talked that much. I idealized her from far, and she never was really sociable.\\

Now, we're at least both conscious of the other existence as a real person. I will certainly never awake any passion in Antiope, and continuing to live by her side will certainly be a regular heart broker.\\

But still, at this moment, we need the other for practical if not sentimental reasons. So time to freeze my feelings, to lock them away and to drop the key.\\

After all, we can probably still be friends.\\

Perhaps.\\

\dcomment{
	To expand and rework. A conclusion must be a lot more memorable
}
